---
title: "01_processed_samples_qaqc"
author: "Peter Flood"
date: "2024-03-04"
output: 
  html_document:
    toc: true
    df_print: paged
    number_sections: true
  html_notebook:
    toc: true
    toc_float: true
    number_sections: true
---

# Load libraries
```{r}
library(tidyverse) #data manipulation
```

# Read in data
Read in raw data and standardize column names
These data are the result of laboratory processing of field samples
```{r}
#read in organic material (om), this is somewhat of a misnomer
#these are basal resources in the food web
processed.om<-read.csv(file = "Data/Processed Samples/Processed_Samples_08_10_2020_om.csv", header = T)
colnames(processed.om)<-c("Date", "Year", "Slough", "Site", "Habitat", "Species", "ID", 
                          "Freezer", "Tube_Weight", "Total_Mass", "Comments", "Sorted", "neg_80_freezer", 
                          "Freeze_Dried", "Dried", "Crushed", "Isotope", "Decarb", "Entered_by", "Checked_by")


#read in and set colnames for invert file
processed.inverts<-read.csv(file = "Data/Processed Samples/Processed_Samples_08_10_2020_inverts.csv", header = T)
colnames(processed.inverts)<-c("Date", "Year", "Season", "Slough", "Site", "Habitat", "Method",
                               "Species", "ID", "Count", "Wet_Weight", "Comments", "Entered_by", "Checked_by", 
                               "Sorted", "neg_80_freezer", "Freeze_Dried", "Dried", "Crushed", "Isotope", "Decarb")

#read in and set colnames for vert file
processed.verts<-read.csv(file = "Data/Processed Samples/Processed_Samples_08_10_2020_verts.csv", header = T)
colnames(processed.verts)<-c("Date", "Year", "Season", "Slough", "Site", "Habitat", "Method",
                             "Species", "ID", "Length", "Wet_Weight", "Sex", "Stomach_Kept",
                             "Comments", "Entered_by", "Checked_by", "Sorted", "neg_80_freezer", 
                             "Freeze_Dried", "Dried", "Crushed", "Isotope", "Decarb")

#make sure there aren't other random columns being read in by selecting on those we want
processed.verts<-select(processed.verts, c(Date, Year, Season, Slough, Site, Habitat, Method,
                                           Species, ID, Length, Wet_Weight, Sex, Stomach_Kept,
                                           Comments, Entered_by, Checked_by, Sorted, neg_80_freezer, 
                                           Freeze_Dried, Dried, Crushed, Isotope, Decarb))

processed.cray<-read.csv(file = "Data/Processed Samples/Processed_Samples_08_10_2020_crayfish.csv", header = T)
colnames(processed.cray)<-c("Date", "Year", "Season", "Slough", "Site", "Habitat",
                            "Method", "Species", "ID", "Length", "Wet_Weight", "Sex", "Comments", "Sorted", "neg_80_freezer",
                            "Freeze_Dried", "Dried", "Crushed", "Isotope", "Decarb", "Entered_by", "Checked_by")

#There's still an issue with reading in these data related to the *s in the excel file
processed.zoo<-read.csv(file = "Data/Processed Samples/Processed_Samples_08_10_2020_zooplankton.csv", header = T)
colnames(processed.zoo)<-c("Month", "Year", "Slough", "Site", "Habitat", "Species", "ID", "Count", "Comments", "Sorted",
                           "neg_80_freezer", "Freeze_Dried", "Dried", "Isotope")


```

# Merge and Organize
Create a new column, Sample_Type, for each data set to allow for easy sorting down the road
```{r}
processed.om$Sample_Type<-"om"
processed.cray$Sample_Type<-"cray"
processed.inverts$Sample_Type<-"invert"
processed.verts$Sample_Type<-"vert"
processed.zoo$Sample_Type<-"zooplankton"
```

Join these data frames together and reorganize
```{r}
#join these data frames together
raw.processed.samples<-bind_rows(processed.om, processed.cray, processed.inverts, 
                                 processed.verts, processed.zoo) %>%
  arrange(Year, Season, Slough, Site, Habitat, Species, Method)

#drop the year column, will reattached
raw.samples.no.year<-select(raw.processed.samples, -Year)
sort(raw.samples.no.year$Date, decreasing = F)
samples.no.date<-filter(raw.samples.no.year, Date=="")

#split the date column into month, day, year 
raw.samples.date.sep<-separate(raw.samples.no.year, col="Date", into = c("Month", "Day", "Year"), sep = "/")

#change this year column to the old year column so that every entry has a year
raw.samples.date.sep$Year<-raw.processed.samples$Year

#check for erroneous values
sort(raw.samples.date.sep$Year, decreasing = T) #shows one entry is 2109, not 2019
sort(raw.samples.date.sep$Year, decreasing = F)

#fixing 2109 error
raw.samples.date.sep$Year[raw.samples.date.sep$Year==2109]<-2019

samples.sorted<-raw.samples.date.sep
```

Need to standardize levels of various factors
Check for data entry errors among factor levels
```{r}
#Month
month.error<-filter(samples.sorted, !Month %in% c(1:12)) 
levels(as.factor(samples.sorted$Month)) #What is in the month column anyway?
#fix month errors
samples.sorted$Month<-replace(samples.sorted$Month, samples.sorted$Month %in% c("2018", "2019"), "")
samples.sorted$Month<-replace(samples.sorted$Month, samples.sorted$Month == "N-18", 11)
samples.sorted$Month[samples.sorted$Year==2019 & grepl("Mi", samples.sorted$ID)]<-3
samples.sorted$Month[samples.sorted$Year==2018 & grepl("Mi", samples.sorted$ID)]<-12
#Set missing months for SRS wet-season sites to March
samples.sorted$Month[samples.sorted$Year==2019 & samples.sorted$Month=="" & samples.sorted$Slough=="SRS"] <- 3
#Set missing months for TSL wet-season sites to April
samples.sorted$Month[samples.sorted$Year==2019 & samples.sorted$Month=="" & samples.sorted$Slough=="TSL"] <- 4
#Set missing months for dry-season samples to November
samples.sorted$Month[samples.sorted$Year==2018 & samples.sorted$Month==""] <- 11


#Day
day.error<-filter(samples.sorted, !Day %in% c(1:31))
levels(as.factor(samples.sorted$Day)) 
#some samples were missing dates
#2019 (dry season) samples from march are being set to the 15th
samples.sorted$Day[samples.sorted$Year==2019 & is.na(samples.sorted$Day) & samples.sorted$Month == 3] <- 15
#Do the same for 2018 (wet season) for each month
samples.sorted$Day[samples.sorted$Year==2018 & is.na(samples.sorted$Day)] <- 15
#TSL 2019


#Year
year.error<-filter(samples.sorted, !Year %in%  c(2018, 2019))

#slough
slough.error<-filter(samples.sorted, !Slough %in% c("TSL", "SRS"))
#2 entries are not labeled as SRS or TSL
#Both are from TSL, fixing that here
samples.sorted$Slough[samples.sorted$Slough %in% c("","PMD", "MDW")]<-"TSL"
#Re-run slough.error to make sure the new output has 0 rows

#Check for season errors
season.error<-filter(samples.sorted, !Season %in% c("WET", "DRY"))

#Set season based on year
samples.sorted$Year<-as.numeric(samples.sorted$Year)
samples.sorted$Season<-as.character(samples.sorted$Season)
samples.sorted$Season[samples.sorted$Year==2018]<-"Wet"
samples.sorted$Season[samples.sorted$Year==2019]<-"Dry"

#Check for any remaining season errors, note capitalization is different
season.error<-filter(samples.sorted, !Season %in% c("Wet", "Dry"))

#Going to do method next, first want to separate TT and the subsequent number 
#This will allow for better calculations of density estimates for TT data if we want to 
#go that route at any point

#First, I need to edit in something between TT and the number to separate by
samples.sorted$Method<-gsub("1", "_1", samples.sorted$Method)
samples.sorted$Method<-gsub("2", "_2", samples.sorted$Method) 
samples.sorted$Method<-gsub("3","_3", samples.sorted$Method)

levels(as.factor(samples.sorted$Method))

#separate method and throw based on "_"
samples.sorted<-separate(samples.sorted, col = "Method", into = c("Method", "Throw"), sep = "_")

#check for throw errors
throw.error<-filter(samples.sorted, Method == "TT" & !Throw %in% c(1,2,3) | Method != "TT" & !is.na(Throw))

#check for method errors
method.error<-filter(samples.sorted, !Method %in% c("EFISH", "TT", "MT", "FR", "DF", "FT"))

#many samples were labelled "HAND" these are organisms and should more accurately be labelled free range
samples.sorted$Method[samples.sorted$Method=="HAND"]<-"FR"
#adding in FT (funnel trap) for zooplankton samples
samples.sorted$Method[grepl("Mi", samples.sorted$ID)]<-"FT"
#organic matter samples don't have a method, these I am also going to label as FR
samples.sorted$Method[is.na(samples.sorted$Method)]<-"FR"
#EFISH spelled as EFSISH, correcting
samples.sorted$Method[samples.sorted$Method=="EFSISH"]<-"EFISH"
#re-run method.error to make sure all error were corrected (0 rows in resulting object)

#now that method is in order, we can work on site
#work on the different levels of Site, if they are not efish, standardize 
#check errors for everything that isn't EFISH, these should all be the the alligator holes/ponds we targeted
#tt = throw trap
tt.site.error<-filter(samples.sorted, !Site %in% c("LJB", "CPB", "AH11", "AH13", "AHWG16", # 5 SRS Sites
                                                "AH02", "AH03", "AH05", "AH09", "AHMDB") & # 5 TSL Sites
                     Method!="EFISH")

levels(as.factor(tt.site.error$Site))

#check general site errors, EFISHing was done at sites besides our focal sites
#They were labeled based on the MDW site or closest MDW site/location
site.error<-filter(samples.sorted, !Site %in% c("LJB", "CPB", "AH11", "AH13", "AHWG16", # 5 SRS Sites
                                                "AH02", "AH03", "AH05", "AH09", "AHMDB"))# 5 TSL Sites
                   

levels(as.factor(site.error$Site))

#remove hyphens from site names
samples.sorted$Site<-gsub("-", "", samples.sorted$Site)

#Correct/ consolidate site names
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="AH WG16", "AHWG16")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="AH2", "AH02")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="AH3", "AH03")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="AH5", "AH05")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="AH9", "AH09")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site %in% c("CATB", "CATPONDB", "AHCFP", "AH CATB"), "CPB")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site %in% c("AHMBD", "AHMDP"), "AHMDB")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site %in% c("LVG16", "WG16"), "AH02")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site %in% c("BJB", "LBJ"), "LJB")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="BJBAH", "AHBJB")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site %in% c("M. DITCH", "MADIERA DITCH"), "MD")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site %in% c("HYDRO E 37>(N)39", "HYDRO E 37.9", 
                                                                             "HYDRO E 37N", "HYDRO E 37N>9", "HYDRO E 37>9"), "37")

samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="TRAIL @ 8A", "8A")
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="MBD", "MDB")



levels(as.factor(samples.sorted$Site))

#re-order column order
samples.sorted<-select(samples.sorted, ID, Species, Sample_Type, Season, Month, Day, Year, Slough, Site, Habitat, 
                       Method, Throw, Length, Wet_Weight, Sex, Stomach_Kept, Comments, everything())

#I already know the habitat variable needs work 
#Look at the various levels to get an idea of how to standardize them
levels(as.factor(samples.sorted$Habitat))

#explore hab levels I'm not immediate sure what they are
misc.hab.samples<-filter(samples.sorted, Habitat %in% c("", "?", "4", "M-NP", "M-P", "MAR-NP", "NP-M")) %>%
  arrange(Habitat)
#all the rows w/o a habitat are EFISH samples, I'll have to label their habitat based on the site label
#Habitat=="?" are minnow traps from BJB, going to leave these, no way to know what the habitat was at this point
#Habitat=="4" must be from efishing in the pond at AHWG16
#M-NP, MAR-NP, and NP-M are the face of the drift fence from the marsh - near pond border facing into the marsh
#will label as marsh
#M-P are the face fo the drift fence from the marsh that face the pond, will label as marsh

#need to investigate what "NP-P" and "P-NP" are too - pretty sure they're NP
p.np.samples<-filter(samples.sorted, Habitat %in% c("NP-P", "P-NP"))
mn.samples<-filter(samples.sorted, Habitat == "MN")
no.hab.samples<-filter(samples.sorted, Habitat == "") #need to come back to these, skipping for now
#these were the face of the drift fence in the near pond that faced into the pond 
#will relabel these to NP
samples.sorted$Habitat<-as.character(samples.sorted$Habitat)

#change various labelling that are all Marsh (Spikerush) to Marsh
samples.sorted$Habitat<-replace(samples.sorted$Habitat, samples.sorted$Habitat %in% 
                                  c("009->10+", "009->10", "E MARSH", "EMARSH", "MARSH", "N->HYDROSTATION", "N->SRS2A", "TRAIL",
                                    "ADJACENT MARSH AND EDGES OF MANGROVE ISLAND", "M-P", "M-NP", "MAR-NP", "NP-M",
                                    "009-10+", "B", "E-MARSH", "MARSH-T3", "MARSH #2", "MARSH 2", "N.HYDROSTATION"
                                  ),
                                "Marsh")

#Change variations of Near Pond to NP
samples.sorted$Habitat<-replace(samples.sorted$Habitat, samples.sorted$Habitat %in% 
                                  c("NEAR POND", "NP", "NP-P", "P-NP", "NEAR POND-T1", "NEAR POND-T2"),
                                "NP")

#Change various labels that represent the drift fence samples that were on the marsh - near pond border to edge
samples.sorted$Habitat<-replace(samples.sorted$Habitat, samples.sorted$Habitat %in% 
                                  c("EDGE", "M-NP", "MAR-NP", "NP-M", "MN"),
                                "Edge")

#Change various labels that all represent Pond
samples.sorted$Habitat<-replace(samples.sorted$Habitat, samples.sorted$Habitat %in% 
                                  c("POND", "CATB", "4", "POND TRAIL", "CREEK", "POND-T1", "POND-T2", "POND-T3", "POND ADJ MARSH",
                                    "POND-MT", "AH"),
                                "Pond")

#Change various labels that represent mangroves to Mangrove
samples.sorted$Habitat<-replace(samples.sorted$Habitat, samples.sorted$Habitat %in% 
                                  c("MANGROVE", "MANG", "MANGROVEROVE"),
                                "Mangrove")

#Change various labels that represent sawgrass ridges to "Sawgrass"
samples.sorted$Habitat<-replace(samples.sorted$Habitat, samples.sorted$Habitat %in% 
                                  c("SAWGRASS", "SAWGRASS MARSH", "SAWGRASS MARSH MARSH"),
                                "Sawgrass")
#fixing the habitat levels for those that are blank based on the site label
#they are all efishing so the site label is distinct for marsh vs pond
#missing that convert to Pond
samples.sorted$Habitat[samples.sorted$Site %in% c("BL-MD-B", "AH59A", "AH-CFP-B", "AH-SC", "AH12L", "AHBJB", "LJB", "CPB")]<-"Pond"


#missing that convert to marsh
samples.sorted$Habitat[samples.sorted$Site %in% c("23A", "HYDRO E 37->(N)39", "HYDRO E 37->9", "TRAIL @8A", '8A', "37", "TSC", 
                                                  "8B", "MDC")]<-"Marsh"

#need to take care of the empty and NA habitat levels, these are all EFISH
#empty - Pond
samples.sorted<-samples.sorted %>% group_by(Habitat) %>% 
  mutate(Habitat = ifelse(any(grepl("AH", Site)) & Habitat == "", "Pond", Habitat))
#NA - Pond
samples.sorted<-samples.sorted %>% group_by(Habitat) %>% 
  mutate(Habitat = ifelse(any(grepl("AH", Site)) & is.na(Habitat), "Pond", Habitat))

#empty - Marsh
samples.sorted<-samples.sorted %>% group_by(Habitat) %>% 
  mutate(Habitat = ifelse(any(!grepl("AH", Site)) & Habitat == "", "Marsh", Habitat))
#NA - Marsh
samples.sorted<-samples.sorted %>% group_by(Habitat) %>% 
  mutate(Habitat = ifelse(any(!grepl("AH", Site)) & is.na(Habitat), "Marsh", Habitat))

#There are some Habitat==NA, looking at what those are here
hab.na<-filter(samples.sorted, is.na(Habitat))


#check levels again, only ?, Marsh, NP, Edge, Pond, Mangrove, and Sawgrass should remain
levels(as.factor(samples.sorted$Habitat))

#after running this, change Site==AHBJB to Site==BJB, I wanted to retain the AH until now to switch the habitat to Pond for those data
samples.sorted$Site<-replace(samples.sorted$Site, samples.sorted$Site=="AHBJB", "BJB")
levels(as.factor(samples.sorted$Site))

#some species IDs are 1 instead of 01 for example, need to correct this
#First need to separate spp abbreviations and ID's, then I can edit the numbers
samples.sorted.Id.split<-separate(samples.sorted, col = ID, into = c("id_abbr", "id_num"), sep = "(?<=[A-Za-z])(?=[0-9])")

#check the levels of id_abbr
levels(as.factor(samples.sorted.Id.split$id_abbr))
filter(samples.sorted.Id.split, id_abbr=="")

#remove * from id_num
samples.sorted.Id.split$id_num<-(gsub("**", "", samples.sorted.Id.split$id_num, fixed = T))
samples.sorted.Id.split$id_num<-(gsub("*", "", samples.sorted.Id.split$id_num, fixed = T))
#check to see if any * remain
sort(samples.sorted.Id.split$id_num, decreasing = F)
sort(samples.sorted.Id.split$id_num, decreasing = T)
#this is a specific sample that has * in the csv file
Mi166<-filter(samples.sorted.Id.split, id_abbr=="Mi" & id_num==166) #looks like they are both gone now
id.ast<-filter(samples.sorted.Id.split, grepl("*", id_num, fixed = T))

samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==1]<-"01"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==2]<-"02"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==3]<-"03"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==4]<-"04"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==5]<-"05"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==6]<-"06"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==7]<-"07"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==8]<-"08"
samples.sorted.Id.split$id_num[samples.sorted.Id.split$id_num==9]<-"09"

#Peri is also abbreviated Pr here, but PR everywhere else, changing to PR
samples.sorted.Id.split$id_abbr[samples.sorted.Id.split$id_abbr=="Pr"]<-"PR"


#recombine id_abbr and id_num into ID
samples.sorted.Id.unite<-unite(samples.sorted.Id.split, col = "ID", c(id_abbr, id_num), sep = "")
#now re-write samples.sorted with this object
samples.sorted<-samples.sorted.Id.unite %>% arrange(Year, Season, Slough, Site, Habitat, Species, ID, Sample_Type)

#Need to organize/consolidate different Species codes
levels(as.factor(samples.sorted$Species))
no.species<-filter(samples.sorted, Species=="") #no idea, this seems like it's a blank row

#wtf is Automeris fabricus?
autfab<-filter(samples.sorted, Species == "AUTOMERIUS FABIRCUS") #no clue... some invert I guess?

#make replacements
samples.sorted$Species<-replace(samples.sorted$Species, samples.sorted$Species=="Peri Sweaters", "PEREPI")
samples.sorted$Species<-replace(samples.sorted$Species, samples.sorted$Species=="Peri Mat", "PERMAT")
samples.sorted$Species<-replace(samples.sorted$Species, samples.sorted$Species=="Peri Sweaters", "PEREPI")
samples.sorted$Species<-replace(samples.sorted$Species, samples.sorted$Species=="Peri", "PERIPH")
samples.sorted$Species<-replace(samples.sorted$Species, samples.sorted$Species %in% c("Algae Ball", "ALGAE BALL"), "ALGBAL")
samples.sorted$Species<-replace(samples.sorted$Species, samples.sorted$Species %in% c("TYHPA", "TYPHA C", "TYPHA/TYSPP", "TYPSPP"), 
                                "TYPDOM")
samples.sorted$Species<-replace(samples.sorted$Species, samples.sorted$Species %in% c("ELECEL J", "ELECEL U"), "ELECEL")
```


## Create Size Class Variable
```{r}
#size classes are only assigned to vertebrate taxa based on length
#standard length for fishes, snout-vent length for herps

#Southern Cricket Frog, 
samples.sorted$size_class[samples.sorted$Species=='ACRIPT']<-'A.gry1'

#Yellow bullhead, Ameiurus natalis 
samples.sorted$size_class[samples.sorted$Species=='AMENAT' & samples.sorted$Length<=96]<-'A.nat1'
samples.sorted$size_class[samples.sorted$Species=='AMENAT' & samples.sorted$Length>96 & samples.sorted$Length<=135]<-'A.nat2'
samples.sorted$size_class[samples.sorted$Species=='AMENAT' & samples.sorted$Length>135 & samples.sorted$Length<=175]<-'A.nat3'
samples.sorted$size_class[samples.sorted$Species=='AMENAT' & samples.sorted$Length>175]<-'A.nat4'
#check to make sure its working 
filter(samples.sorted, Species == 'AMENAT') %>% select(size_class) #checks out

#Brown bullhead, Ameiurus nebulosus 
samples.sorted$size_class[samples.sorted$Species=='AMENEB' & samples.sorted$Length<=96]<-'A.neb1'
samples.sorted$size_class[samples.sorted$Species=='AMENEB' & samples.sorted$Length>96 & samples.sorted$Length<=135]<-'A.neb2'
samples.sorted$size_class[samples.sorted$Species=='AMENEB' & samples.sorted$Length>135 & samples.sorted$Length<=175]<-'A.neb3'
samples.sorted$size_class[samples.sorted$Species=='AMENEB' & samples.sorted$Length>175]<-'A.neb4'

#Bowfin, Amia calva
samples.sorted$size_class[samples.sorted$Species=='AMICAL' & samples.sorted$Length<=70]<-'A.cal1'
samples.sorted$size_class[samples.sorted$Species=='AMICAL' & samples.sorted$Length>70]<-'A.cal2'

#Oscar, Astronotus ocellatus
samples.sorted$size_class[samples.sorted$Species=='ASTOCE']<-'A.oce1'

#Two-toed Amphiuma, Amphiuma means
samples.sorted$size_class[samples.sorted$Species=='AMPMEA']<-'A.mea1'

#American Eel, Anguilla rostrata
samples.sorted$size_class[samples.sorted$Species=='ANGROS']<-'A.ros1'

#Pirate Perch, Aphredoderus sayanus
samples.sorted$size_class[samples.sorted$Species=='APHSAY']<-'A.say1'

#Pike killifish, Belonesox belizanus
samples.sorted$size_class[samples.sorted$Species=='BELBEL' & samples.sorted$Length<=64]<-'B.bel1'
samples.sorted$size_class[samples.sorted$Species=='BELBEL' & samples.sorted$Length>64]<-'B.bel2'

#Black Acara, Cichlasoma bimaculatum
samples.sorted$size_class[samples.sorted$Species=='CICBIM']<-'C.bim1'

#Jaguar Guapote, Cichlasoma managuense
samples.sorted$size_class[samples.sorted$Species=='CICMAN']<-'C.man1'

#Peacock Bass, Cichlasoma ocellaris
samples.sorted$size_class[samples.sorted$Species=='CICOCE']<-'C.oce1'

#Mayan Cichlid, Cichlasoma urophthalmus
samples.sorted$size_class[samples.sorted$Species=='CICURO' & samples.sorted$Length<=120]<-'C.uro1'
samples.sorted$size_class[samples.sorted$Species=='CICURO' & samples.sorted$Length>120]<-'C.uro2'

#Walking Catfish, Clarias batrachus
samples.sorted$size_class[samples.sorted$Species=='CLABAT']<-'C.bat1'

#Sheepshead Minnow, Cyprinodon variegatus
samples.sorted$size_class[samples.sorted$Species=='CIPVAR']<-'C.var1'

#Everyglades Pygmy Sunfish, Elassoma evergladei
samples.sorted$size_class[samples.sorted$Species=='ELAEVE']<-'E.eve1'

#Bluespotted Sunfish, Enneacanthus gloriosus
samples.sorted$size_class[samples.sorted$Species=='ENNGLO']<-'E.glo1'

#Lake Chubsucker, Erimyzon sucetta
#Two ERISUC weren't measured but estimated lengths are in the comments
#adding those lengths into the lengths column so they can have a size class
samples.sorted$Length[samples.sorted$ID %in% c('EU01', 'EU02')]<-c(50, 98)
#create size classes
samples.sorted$size_class[samples.sorted$Species=='ERISUC' & samples.sorted$Length<=100]<-'E.suc1'
samples.sorted$size_class[samples.sorted$Species=='ERISUC' & samples.sorted$Length>100 & 
                           samples.sorted$Length<=150]<-'E.suc2'
samples.sorted$size_class[samples.sorted$Species=='ERISUC' & samples.sorted$Length>150]<-'E.suc3'

#Golden Topminnow, Fundulus chrysotus
samples.sorted$size_class[samples.sorted$Species=='FUNCHR' & samples.sorted$Length<=40]<-'F.chr1'
samples.sorted$size_class[samples.sorted$Species=='FUNCHR' & samples.sorted$Length>40]<-'F.chr2'

#Redfin Pickerel, Esox americanus 
samples.sorted$size_class[samples.sorted$Species=='ESOAME']<-'E.ame1'

#Marsh Killifish, Fundulus confluentus
samples.sorted$size_class[samples.sorted$Species=='FUNCON']<-'F.con1'

#Eastern Mosquitofish, Gambusia holbrooki
samples.sorted$size_class[samples.sorted$Species=='GAMHOL' & samples.sorted$Length<=17]<-'G.hol1'
samples.sorted$size_class[samples.sorted$Species=='GAMHOL' & samples.sorted$Length>17]<-'G.hol2'

#African Jewelfish, Hemicrhomis letourneuxi
samples.sorted$size_class[samples.sorted$Species=='HEMLET']<-'H.let1'

#Least Killifish, Heterandria formosa
samples.sorted$size_class[samples.sorted$Species=='HETFOR' & samples.sorted$Length<=12]<-'H.for1'
samples.sorted$size_class[samples.sorted$Species=='HETFOR' & samples.sorted$Length>12]<-'H.for2'

#Brown Hoplo, Hoplosternum littorale 
samples.sorted$size_class[samples.sorted$Species=='HOPLIT']<-'H.lit1'

#Flagfish, Jordanella floridae
samples.sorted$size_class[samples.sorted$Species=='JORFLO' & samples.sorted$Length<=18]<-'J.flo1'
samples.sorted$size_class[samples.sorted$Species=='JORFLO' & samples.sorted$Length>18]<-'J.flo2'

#Brook Silverside, Labidesthes sicculus
samples.sorted$size_class[samples.sorted$Species=='LABSIC']<-'L.sic1'

#Florida Gar, Lepisosteus platyrhincus
samples.sorted$size_class[samples.sorted$Species=='LEPPLA' & samples.sorted$Length<=450]<-'L.pla1'
samples.sorted$size_class[samples.sorted$Species=='LEPPLA' & samples.sorted$Length>450]<-'L.pla2'

#Warmouth, Lepomis gulosus
samples.sorted$size_class[samples.sorted$Species=='LEPGUL' & samples.sorted$Length<=71]<-'L.gul1'
samples.sorted$size_class[samples.sorted$Species=='LEPGUL' & samples.sorted$Length>71 & 
                           samples.sorted$Length<=95]<-'L.gul2'
samples.sorted$size_class[samples.sorted$Species=='LEPGUL' & samples.sorted$Length>95 & 
                           samples.sorted$Length<=120]<-'L.gul3'
samples.sorted$size_class[samples.sorted$Species=='LEPGUL' & samples.sorted$Length>120]<-'L.gul4'

#Bluegill, Lepomis macrochirus
samples.sorted$size_class[samples.sorted$Species=='LEPMAC']<-'L.mac1'

#Dollar Sunfish, Lepomis marginatus
samples.sorted$size_class[samples.sorted$Species=='LEPMAR']<-'L.mar1'

#Redear Sunfish, Lepomis microlophus
#some LEPMIC have a space after LEPMIC in the species column and are omitted
#correction for that
samples.sorted$Species[samples.sorted$Species=='LEPMIC ']<-'LEPMIC'
#size classes
samples.sorted$size_class[samples.sorted$Species=='LEPMIC' & samples.sorted$Length<=100]<-'L.mic1'
samples.sorted$size_class[samples.sorted$Species=='LEPMIC' & samples.sorted$Length>100]<-'L.mic2'

#Spotted Sunfish, Lepomis punctatus
samples.sorted$size_class[samples.sorted$Species=='LEPPUN' & samples.sorted$Length<=40]<-'L.pun1'
samples.sorted$size_class[samples.sorted$Species=='LEPPUN' & samples.sorted$Length>40 & 
                           samples.sorted$Length<=90]<-'L.pun2'
samples.sorted$size_class[samples.sorted$Species=='LEPPUN' & samples.sorted$Length>90]<-'L.pun3'

#Bluefin Killifish, Lucania goodei
samples.sorted$size_class[samples.sorted$Species=='LUCGOO' & samples.sorted$Length<=17.5]<-'L.goo1'
samples.sorted$size_class[samples.sorted$Species=='LUCGOO' & samples.sorted$Length>17.5]<-'L.goo2'

#Peacock Eel, Macrognathus siamensis
samples.sorted$size_class[samples.sorted$Species=='MACSIA']<-'M.sia1'

#Largemouth Bass, Micropterus salmoides
samples.sorted$size_class[samples.sorted$Species=='MICSAL']<-'M.sal1'

#Inland Silverside, Menidia berylina
samples.sorted$size_class[samples.sorted$Species=='MENBER']<-'M.ber1'

#Asian Swwamp Eel, Monopterus albus
#distribution of sizes
monalb<-filter(samples.sorted, Species == 'MONALB')
hist(monalb$Length)

#create size classes
samples.sorted$size_class[samples.sorted$Species=='MONALB' & samples.sorted$Length<=275]<-'M.alb1'
samples.sorted$size_class[samples.sorted$Species=='MONALB' & samples.sorted$Length>275 & 
                           samples.sorted$Length<=450]<-'M.alb2'
samples.sorted$size_class[samples.sorted$Species=='MONALB' & samples.sorted$Length>450 & 
                           samples.sorted$Length<=625]<-'M.alb3'
samples.sorted$size_class[samples.sorted$Species=='MONALB' & samples.sorted$Length>625]<-'M.alb4'

#Florida Green Water Snake, Nerodia floridana
samples.sorted$size_class[samples.sorted$Species=='NERFLO']<-'N.flo1'

#Tadpole Madtom, Noturus gyrinus
samples.sorted$size_class[samples.sorted$Species=='NOTGYR']<-'N.gyr1'

#Coastal Shiner, Notropis petersoni
samples.sorted$size_class[samples.sorted$Species=='NOTPET']<-'N.pet1'

#Peninsula Newt, Notophthalmus viridescens
samples.sorted$size_class[samples.sorted$Species=='NOTVIR']<-'N.vir1'

#Blue Tilapia, Oreochromis aureus
samples.sorted$size_class[samples.sorted$Species=='OREAUR']<-'O.aur1'

#Sailfin Molly, Poecilia latipinna
samples.sorted$size_class[samples.sorted$Species=='POELAT' & samples.sorted$Length<=20]<-'P.lat1'
samples.sorted$size_class[samples.sorted$Species=='POELAT' & samples.sorted$Length>20]<-'P.lat2'

#Everglades Pygmy Siren, Psuedobranchus axanthus
samples.sorted$size_class[samples.sorted$Species=='PSEAXA']<-'P.axa1'

#Pig Frog, Rana grylio
samples.sorted$size_class[samples.sorted$Species=='RANATP']<-'R.gry1'
samples.sorted$size_class[samples.sorted$Species=='RANGRY']<-'R.gry2'

#Greater Siren, Sirens lacertina
samples.sorted$size_class[samples.sorted$Species=='SIRLAC']<-'S.lac1'

#Spotted Tilapia, Tilapia mariae
samples.sorted$size_class[samples.sorted$Species=='TILMAR']<-'T.mar1'

#Snook
samples.sorted$size_class[samples.sorted$Species=="SNOOK"]<-"C.und1"

#Look for rows that still don't have a size class - should only have empcups or damaged specimens
size_class.error<-filter(samples.sorted, is.na(size_class) & Sample_Type=="vert")
```
Export Cleaned Data
```{r}
#sort and write out to csv
samples.sorted %>% arrange(Year, Season, Slough, Site, Habitat, Species, ID, size_class, Sample_Type) %>%
    write.csv(file = "Outputs/Processed Samples/processed_samples_qaqc.csv", row.names = F)

sample.size<-samples.sorted %>% group_by(Year, Species) %>% summarise(n=n())

write.csv(sample.size, file = "Outputs/Processed Samples/sample_size_year_species.csv", row.names = F)

#To facilitate looking at output
samples.sorted<-samples.sorted %>% arrange(Year, Species, Slough, Habitat, Site)

#Examining a couple specific groups
tilmar.2018<-samples.sorted %>% filter(Species=="TILMAR", Year==2018) %>% 
  arrange(ID)

belbel<-samples.sorted %>% filter(Species == "BELBEL")

```
