---
title: "04_trophic_positions_from_stomach_contents"
author: "Peter Flood"
date: "2024-03-04"
output: 
  html_document:
    toc: true
    df_print: paged
    number_sections: true
  html_notebook:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Libraries
```{r}
library(tidyverse)
library(openxlsx)
library(RVAideMemoire)
library(lmPerm)
library(rcompanion)
```

# Read in data
```{r}
#Using merged stomach counts 
#which is output from previous scripts
stomach.counts <- read.csv("Outputs/Stomach Contents/stomachs_count_merge.csv")
```

# Calculate individual trophic positions

```{r}
#Remove covariates aside from size class, habitat, season, and slough and remove empty stomachs
no.empty.stomachs <- stomach.counts %>% 
  filter(Empty == 0) %>% 
  select(-c(ID, Species, Year, Site, Length, Wet_Weight, Sex, Empty))

#number of empty stomachs
nrow(stomach.counts)-nrow(no.empty.stomachs)
#238

#create vector of diet item trophic positions in the same order as the columns in no.empty.stomachs
diet.item.trophp <- c(1.5, 2, 2, 2, 2.5, 1.5, 1.5, 1.5, 1, 1.5, 2.37, 0.2, 1.5, 1, 0, 2, 2, 1.5, 1.5, 2.5, 1.5, 1, 2, 1.5, 1.5, 2, #ends with Palaemonetes
                      0, 2, 1.5, 0)
names(diet.item.trophp) <- colnames(no.empty.stomachs)[5:34]
#calculate trophic positions with equation from Adams et al 1983 like in Flood et al 2022
#TrophP = 1 + sum(trophp[prey]*proportion of diet of prey item)

#remove covariates
all.com <- no.empty.stomachs %>% select(-c(size_class, Season, Slough, Habitat))

#create prey proportion matrix
#first, calculate row sum
prey.sums <- apply(all.com, 1, sum)

#create matrix to write over
prey.pro<-all.com

#Write loop to calculate prey proportions and write over the matrix we just made
for(i in 1:nrow(all.com)){
  for(j in 1:ncol(all.com)){
    prey.pro[i,j]<-all.com[i,j]/prey.sums[i]
  }
}

prey.pro[is.na(prey.pro)]<-0

#check rows sum to one to be sure the loop worked correctly
all.com.check<-apply(prey.pro, 1, sum)
sort(all.com.check, decreasing = F)
all.com.check[is.na(all.com.check)]
sum(all.com.check)==nrow(all.com)

#prey proportion * prey trophic position
prey.pro.troph<-diet.item.trophp*prey.pro

#take the sum, add 1
all.com.trophp<-apply(prey.pro.troph, 1, sum)+1 %>% round(3)
all.com.trophp.na<-all.com.trophp[is.na(all.com.trophp)]
```

# Compare across size classes, habitats, seasons, and sloughs
```{r}
#data formatting and prep for statistical analysis
#isolate covariates
covariates <- no.empty.stomachs %>% select(size_class, Season, Slough, Habitat)
#re-attach covariates
all.trophp <- bind_cols(covariates, all.com.trophp)
colnames(all.trophp) <- c(colnames(covariates), "Trophic_Position")

#sample size per level
all.trophp.n<-all.trophp %>% group_by(size_class, Season, Slough, Habitat) %>% tally()

#drop levels where n < 5
all.trophp.5<-all.trophp %>% group_by(size_class, Season, Slough, Habitat) %>% filter(n()>4) %>% ungroup()
#new sample size table
all.trophp.5.n<-all.trophp.5 %>% group_by(size_class, Season, Slough, Habitat) %>% tally()
```

## Permuted ANOVA
```{r}
#Test assumption of normality - likely violated
#library(RVAideMemoire)
byf.shapiro(Trophic_Position ~ size_class, all.trophp.5) 
byf.shapiro(Trophic_Position ~ Season, all.trophp.5) 
byf.shapiro(Trophic_Position ~ Slough, all.trophp.5) 
byf.shapiro(Trophic_Position ~ Habitat, all.trophp.5) 

#Both Trophic Position and log(Trophic Position) have non-normal groups for all factors
#proceed with permuted ANOVA
#library(lmPerm)
trophp.5.aovp<-aovp(Trophic_Position ~ size_class*Habitat*Season*Slough, data = all.trophp.5, perm = "Exact")
aovp.summary<-summary(trophp.5.aovp)[[1]]
write.xlsx(aovp.summary, file = "Outputs/Stomach Contents/Trophic Position/Post-Invasion/aovp_summary.xlsx")
```

## Post-hoc comparisons
```{r}
#pairwise permutation test
#library(rcompanion)
trophp.5.unite<-all.trophp.5 %>% unite(col = "ont_habdate", c("size_class", "Habitat", "Season", "Slough"), sep = "_")

pairwise.trophp<-pairwisePermutationTest(formula = Trophic_Position ~ ont_habdate, data = trophp.5.unite) 

pairwise.trophp<-pairwise.trophp %>% arrange(p.value)
```

### Reformat post-hoc test output
```{r}
#reformat to separate ont_habdate comparison column into its constituents 
pairwise.trophp.sep<-pairwise.trophp %>% separate(Comparison, into = c("A", "B"), sep = " - ") %>% 
  separate(A, into = c("Size Class A", "Habitat A", "Season A", "Slough A"), sep = "_") %>% 
  separate(B, into = c("Size Class B", "Habitat B", "Season B", "Slough B"), sep = "_") %>% 
  mutate(`Slough B` = gsub(" = 0", "", `Slough B`)) %>% 
  arrange(`Size Class A`, `Habitat A`, `Season A`, `Slough A`, `Size Class B`, `Habitat B`, `Season B`, `Slough B`) 

#separate out certain kinds of comparisons w/in each slough
#and then filter for comparisons where p <=0.05
#habitat comparisons
habitat.shifts <- pairwise.trophp.sep %>% filter(`Size Class A` == `Size Class B` & `Slough A` == `Slough B` &
                                                   `Season A` == `Season B`)
habitat.shifts.05 <- habitat.shifts %>% filter(p.value <= 0.06)

#season comparisons
season.shifts <- pairwise.trophp.sep %>% filter(`Size Class A` == `Size Class B` & `Slough A` == `Slough B` &
                                                   `Habitat A` == `Habitat B`)
season.shifts.05 <- season.shifts %>% filter(p.value <= 0.06)

#slough comparison
slough.shifts <- pairwise.trophp.sep %>% filter(`Size Class A` == `Size Class B` & `Habitat A` == `Habitat B` &
                                                   `Season A` == `Season B`)
slough.shifts.05 <- slough.shifts %>% filter(p.value <= 0.06)

#size_class shifts
size.class.shifts <- pairwise.trophp.sep %>% separate(col = `Size Class A`, into = c("Species A", "Size Class A"),
                                                      sep = "(?<=[A-Za-z])(?=[0-9])") %>% 
  separate(col = `Size Class B`, into = c("Species B", "Size Class B"),
           sep = "(?<=[A-Za-z])(?=[0-9])") %>% 
  filter(`Species A` == `Species B` & `Habitat A` == `Habitat B` &
           `Season A` == `Season B` & `Slough A` == `Slough B`) %>% 
  unite(col = "Size Class A", c(`Species A`, `Size Class A`), sep = "") %>% 
  unite(col = "Size Class B", c(`Species B`, `Size Class B`), sep = "")

size.class.shifts.05 <- size.class.shifts %>% filter(p.value <=0.06)

#all shifts in trophic position with p <= 0.055
trophic_position_shifts <- pairwise.trophp.sep %>% filter(p.value <= 0.06)

#make a list of the different comparisons and export to excel
trophic.comarisons.05 <- list("Size Class Shifts" = size.class.shifts.05, "Slough Shifts" = slough.shifts.05,
                              "Habitat Shifts" = habitat.shifts.05, "Season Shifts" = season.shifts.05,
                              "All Shifts" = trophic_position_shifts)
write.xlsx(trophic.comarisons.05, 
           file = "Outputs/Stomach Contents/Trophic Position/Post-Invasion/significant_trophic_position_comparisons.xlsx")
```

# Mean & SD trophic position per habitat/season/slough
```{r}
#calculate mean and sd per size class per habitat per season per slough
all.trophp.mean.sd <- all.trophp %>% group_by(size_class, Slough, Season, Habitat) %>% 
  summarise(Mean_Trophic_Position = mean(Trophic_Position), SD_Trophic_Position = sd(Trophic_Position)) %>% 
  bind_cols(all.trophp.n$n)

colnames(all.trophp.mean.sd) <- c(colnames(all.trophp.mean.sd)[1:6], "N")

write.xlsx(all.trophp.mean.sd, "Outputs/Stomach Contents/Trophic Position/Post-Invasion/all_post-invasion_trophic_positions.xlsx")
```
# Pre- vs Post-Invasion Comparisons

The pre-invasion tropic positions are from Flood et al. 2023 - https://doi.org/10.1016/j.fooweb.2022.e00265
Raw data and associated code that creates the below data frame are available through the Florida Coastal Everglades Long-term Ecological Research site website (https://fcelter.fiu.edu/data/) and are data package FCE1263_Flood_StableIsotopesStomachContents

For convenience, the below data frame is also archived with the data package associated with this script: FCE1259_Flood_StableIsotopesStomachContents

## Pre-invasion load and format data
```{r}
#load data
pre.trophp <- read.csv("Data/Stomach Contents/FCE1259_pre-invasion_individual_trophic_positions.csv")

#format
pre.trophp.formatted <- pre.trophp %>% filter(Ont_Class != 0, !HabDate %in% c("Cladium1", "Cladium2")) %>% 
  separate(col = HabDate, into = c("Habitat", "Season"), sep = "(?<=[A-Za-z])(?=[0-9])") %>% 
  mutate(Habitat = gsub("Eleocharis", "Marsh", Habitat)) %>% 
  mutate(Season = case_when(Season == 1 ~ "Wet", Season == 2 ~ "Dry")) %>% 
  separate(col = Ont_Class, into = c("Species", "Size_Class"), sep = "(?<=[A-Za-z])(?=[0-9])")

#need to make sure species that weren't assigned a size class in the historic data have one now
#all those missing only have 1 size class option
pre.no.size.class <- pre.trophp.formatted %>% filter(is.na(Size_Class))

#list of size classes for pre and post invasion data
levels(as.factor(all.trophp$size_class)) #post-invasion
levels(as.factor(pre.no.size.class$Species)) #pre-invasion spp w/o a size class designation

#assign size classes to those that do not have one
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="A_cal"] <- 2
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="A_xen"] <- 1 #none collected during post-invasion work
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="C_bat"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="C_bim"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="C_var"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="E_eve"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="E_fus"] <- 1 #none collected during post-invasion work
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="E_glo"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="L_mac"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="L_mar"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="L_sic"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="M_sal"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="N_cry"] <- 1 #none collected during post-invasion work
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="N_gyr"] <- 1 
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="N_mac"] <- 1 #none collected during post-invasion work
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="N_pet"] <- 1
pre.trophp.formatted$Size_Class[pre.trophp.formatted$Species=="T_mar"] <- 1

#re-run this code
pre.no.size.class <- pre.trophp.formatted %>% filter(is.na(Size_Class)) #0 rows means we got them all

#unite species and size class columns and add column to denote pre-invasion
pre.trophp.unite <- pre.trophp.formatted %>% unite("size_class", c(Species, Size_Class), sep = "") %>% 
  mutate(Invasion_Status = "Pre-Invasion") %>% 
  mutate(Trophic_Position = TrophP) %>% 
  select(-c(TrophP)) %>% 
  select(size_class, Season, Habitat, Trophic_Position, Invasion_Status) %>% 
  mutate(size_class = gsub("_", ".", size_class))

#reformat all.trophp to match pre.trophp.unite
#Also need to drop Taylor Slough data
post.trophp <- all.trophp %>% filter(Slough == "SRS") %>% select(-c(Slough)) %>% 
  mutate(Invasion_Status = "Post-Invasion")

#combine and condense covariates 
pre.post.trophp <- bind_rows(pre.trophp.unite, post.trophp)
#drop any groups where n < 5
pre.post.trophp.5 <- pre.post.trophp %>% group_by(size_class, Season, Habitat, Invasion_Status) %>% filter(n()>4) %>% ungroup()
```

## Permuted ANOVA

Check assumptions of normality
```{r}
#Test assumption of normality for ANOVA
#library(RVAideMemoire)
byf.shapiro(Trophic_Position ~ size_class, pre.post.trophp.5) 
byf.shapiro(Trophic_Position ~ Season, pre.post.trophp.5)
byf.shapiro(Trophic_Position ~ Habitat, pre.post.trophp.5) 
byf.shapiro(Trophic_Position ~ Invasion_Status, pre.post.trophp.5) 
#Both Trophic Position and log(Trophic Position) have non-normal groups for all factors
#proceed with permuted ANOVA
```

Permuted ANOVA 
```{r}
#library(lmPerm)
pre.post.trophp.5.aovp <- aovp(Trophic_Position ~ size_class*Habitat*Season*Invasion_Status, data = pre.post.trophp.5, perm = "Exact")
pre.post.aovp.summary <- summary(pre.post.trophp.5.aovp)[[1]]
write.xlsx(pre.post.aovp.summary, 
           file = "Outputs/Stomach Contents/Trophic Position/Pre-vs-Post-Invasion/pre_post_aovp_summary.xlsx")
```

### Post-hoc pairwise permutation test
Functionally similar to Tukey's HSD
```{r}
#pairwise permutation test
#library(rcompanion)
pre.post.trophp.5.unite <- pre.post.trophp.5 %>% 
  unite(col = "ont_habdate_invasion", c("size_class", "Habitat", "Season", "Invasion_Status"), sep = "_")

pre.post.pairwise.trophp <- pairwisePermutationTest(formula = Trophic_Position ~ ont_habdate_invasion, data = pre.post.trophp.5.unite) 

pre.post.pairwise.trophp <- pre.post.pairwise.trophp %>% arrange(p.value)
```

Reformat post-hoc output
```{r}
#reformat to separate ont_habdate comparison column into its constituents 
pre.post.pairwise.trophp.sep <- pre.post.pairwise.trophp %>% separate(Comparison, into = c("A", "B"), sep = " - ") %>% 
  separate(A, into = c("Size Class A", "Habitat A", "Season A", "Invasion Status A"), sep = "_") %>% 
  separate(B, into = c("Size Class B", "Habitat B", "Season B", "Invasion Status B"), sep = "_") %>% 
  mutate(`Invasion Status B` = gsub(" = 0", "", `Invasion Status B`)) %>% 
  arrange(`Size Class A`, `Habitat A`, `Season A`, `Invasion Status A`, `Size Class B`, `Habitat B`, `Season B`, `Invasion Status B`) 

#separate out certain kinds of comparisons w/in each slough
#and then filter for comparisons where p <=0.05
#pre/post shift in trophic position
pre.post.shifts <- pre.post.pairwise.trophp.sep %>% filter(`Size Class A` == `Size Class B` & `Habitat A` == `Habitat B` &
                                                   `Season A` == `Season B`) %>% arrange(p.value)

pre.post.shifts.05 <- pre.post.shifts %>% filter(p.value <= 0.06)

#post-invasion shifts among habitats and seasons
#habitat comparisons
post.habitat.shifts <- pre.post.pairwise.trophp.sep %>% filter(`Invasion Status A` == `Invasion Status B` &
                                                               `Size Class A` == `Size Class B` & 
                                                                 `Season A` == `Season B`) %>% arrange(p.value) %>% 
                                                        filter(`Invasion Status A` == "Post-Invasion")

post.habitat.shifts.05 <- post.habitat.shifts %>% filter(p.value <= 0.06)

#season comparisons
post.season.shifts <- pre.post.pairwise.trophp.sep %>% filter(`Invasion Status A` == `Invasion Status B` &
                                                                 `Size Class A` == `Size Class B` & 
                                                                 `Habitat A` == `Habitat B`) %>% arrange(p.value) %>% 
  filter(`Invasion Status A` == "Post-Invasion")

post.season.shifts.05 <- post.season.shifts %>% filter(p.value <= 0.06)


#size_class shifts
post.size.class.shifts <- pre.post.pairwise.trophp.sep %>% separate(col = `Size Class A`, into = c("Species A", "Size Class A"),
                                                      sep = "(?<=[A-Za-z])(?=[0-9])") %>% 
  separate(col = `Size Class B`, into = c("Species B", "Size Class B"),
           sep = "(?<=[A-Za-z])(?=[0-9])") %>% 
  filter(`Species A` == `Species B` & `Habitat A` == `Habitat B` &
           `Season A` == `Season B` & `Invasion Status A` == "Post-Invasion" & 
           `Invasion Status B` == "Post-Invasion") %>% 
  unite(col = "Size Class A", c(`Species A`, `Size Class A`), sep = "") %>% 
  unite(col = "Size Class B", c(`Species B`, `Size Class B`), sep = "")

post.size.class.shifts.05 <- post.size.class.shifts %>% filter(p.value <=0.06)

#all shifts in trophic position with p <= 0.055
pre.post.trophic.position.shifts <- pre.post.pairwise.trophp.sep %>% filter(p.value <= 0.06)

#make a list of the different comparisons and export to excel
pre.post.trophic.comarisons.05 <- list("Pre_Post Shifts" = pre.post.shifts, "Size Class Shifts" = post.size.class.shifts.05,
                              "Habitat Shifts" = post.habitat.shifts.05, "Season Shifts" = post.season.shifts.05,
                              "All Shifts" = pre.post.trophic.position.shifts)
write.xlsx(pre.post.trophic.comarisons.05, 
           file = "Outputs/Stomach Contents/Trophic Position/Pre-vs-Post-Invasion/pre_post_trophic_position_comparisons.xlsx")
```

## Post-invasion mean & SD trophic position
```{r}
#calculate mean and sd per size class per habitat per season per slough
#sample size
pre.post.trophp.n <-  pre.post.trophp %>% group_by(size_class, Invasion_Status, Season, Habitat) %>% tally()
#mean & sd
pre.post.trophp.mean.sd <- pre.post.trophp %>% group_by(size_class, Invasion_Status, Season, Habitat) %>% 
  summarise(Mean_Trophic_Position = mean(Trophic_Position), SD_Trophic_Position = sd(Trophic_Position)) %>% 
  bind_cols(pre.post.trophp.n$n)
#change colnames
colnames(pre.post.trophp.mean.sd) <- c(colnames(pre.post.trophp.mean.sd)[1:6], "N")
```

#Identify pre- vs post-invasion trophic positions shifts
```{r}
#condense pre.post.shifts columns to prepare to merge with pre.post.trophp.mean.sd
pre.post.shifts.unite <- pre.post.shifts %>% unite("ont_habdate", c(`Size Class A`, `Habitat A`, `Season A`))

#wide form w/ psuedo F and p-value
pre.post.trophp.wide <- pre.post.trophp.mean.sd %>%
  #mutate(across(Stat:p.value, round, 2))
  unite("Trophic_Position",
      c(Mean_Trophic_Position, SD_Trophic_Position),
      sep = " \u00B1 ") %>%
  pivot_wider(names_from = Invasion_Status,
              values_from = c(Trophic_Position, N)) %>%
  unite("ont_habdate", c(size_class, Habitat, Season)) %>%
  merge(., pre.post.shifts.unite, by = "ont_habdate", all.x = T) %>%
  select(
    ont_habdate,
    `N_Post-Invasion`,
    `Trophic_Position_Post-Invasion`,
    `N_Pre-Invasion`,
    `Trophic_Position_Pre-Invasion`,
    Stat,
    p.value
  ) %>%
  mutate(Stat = as.numeric(Stat),
         p.value = as.numeric(p.value)) %>% 
  #mutate(across(Stat:p.value), round, 2) %>%
  separate(ont_habdate,
           into = c("Size Class", "Habitat", "Season"),
           sep = "_") 

pre.post.wide.stat <- pre.post.trophp.wide %>% filter(!is.na(p.value))

pre.post.wide.stat.05 <- pre.post.wide.stat %>% filter(p.value < 0.06)    

#export to excel
write.xlsx(list("All_Pre_Post" = pre.post.trophp.wide, "Pre_Post_with_Stats" = pre.post.wide.stat, "Pre_Post_Significant" = pre.post.wide.stat.05), 
           file = "Outputs/Stomach Contents/Trophic Position/Pre-vs-Post-Invasion/pre_post_mean_sd_trophp_stats.xlsx")
```



















